---
title: "Statistics of the industry"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(rvest) # to scrape wikipedia page
```

# Analysis of movies- IMDB dataset

For all of you movie fans out there, this section is analysing some basic statistics about all of your favourite movies!
  
The dataset contains 2961 of the most successful movies.
 
  Let's see their distribution by genre:
```{r, echo=FALSE, warning=FALSE, message=FALSE}

movies <- read_csv(here::here("data", "movies.csv"))
movies %>% 
  group_by(genre) %>% 
  count(sort=TRUE)

```
It appears that most of them are comedies, followed by action movies (any Avengers fans?), Drama, Adventure and Crime. 

Now, let's see which genre provides a higher return on budget:

```{r, echo=FALSE }
movies %>% 
  group_by(genre) %>%
  summarise(average_gross=mean(gross),average_budget=mean(budget),return_on_budget=average_gross/average_budget) %>% 
arrange(desc(return_on_budget))
```

Musicals appear to be making a higher return which is mainly driven by the fact that they are the cheaper type of movies to produce.

Now, let's name drop a bit. Who do you think is the highest grossing director ? 

```{r, echo=FALSE}
movies %>% 
group_by(director) %>%
  summarise(sgross=sum(gross),average_gross=mean(gross),median_gross=median(gross),sd_gross=sd(gross)) %>% 
slice_max(order_by = sgross, n=15) 

```

Unsurprinsgly, our buddy Spielberg tops the ranking. Unpopular opinion: I'm not a big fan of his films...

Finally, ratings. Let's try to find out whether critics are snobs: 

```{r, echo=FALSE}
movies %>% 
group_by(genre) %>%
  summarise(av_rating=mean(rating)) %>%  
arrange(desc(av_rating))

```
I think it's safe to say that they are, right?


Next question: is the budget allocated to produce a movie driving its income?

```{r, gross_on_budget}

movies %>% 
ggplot(aes(x = gross, y = budget)) +
  geom_point(alpha=0.2) +
  geom_smooth(method = "lm") 

```
  
